Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-29 main-disk-model.tex
more description of the approach, also abt lazy writes

@@

In the first step, we order the tasks by non-increasing ranks (e.g. their bottom levels).
In the next step, we repeatedly schedule ready tasks.
For each task, we first choose the best processor to put it on - the one that minimizes the expected finishing time.
For each processor, we compute this earliest finishing time by first calculating the earliest starting time on this processor.
    It is computed as the maximum of the ready time of computation on this processor, and the time to read input files.

>>>>

\skug{Todo: describe deviations}

@@

In the first step, we order the tasks by non-increasing ranks (e.g. their bottom levels).
In the next step, we repeatedly schedule ready tasks.
For each task, we first choose the best processor to put it on - the one that minimizes the expected finishing time.
For each processor, we compute this earliest finishing time by first calculating the earliest starting time on this processor.
It is computed as the maximum of the ready time of computation on this processor, and the time to read input files.
For the currently reviewed processor, we preliminarily schedule necessary file writes on other processors holding input files,
and file reads on the current processor.
Doing so, we respect the ready times on writes on other processors and reads on the current processor.
We possibly plan ``into the past'' with ready and writes.

The earliest finish time is calculated by adding the execution time (possibly with delay due to memory overflow) to the start time.
Further scheduling decisions happen when another task finishes.
\skug{check this: when a task finishes earlier or later than planned, we review our earlier scheduling decisions and may
move the task execution to another processor if this proves more beneficial.}

When a task finishes, we look at all of its sucessors, rather than only the ready ones.
For tasks that lie further in the future, we try to plan rather early.
Therefore, we employ lazy writes.
We try to write the files for these tasks to the disk early.
So, we preliminarily schedule these file writes. However, they are not high priority and can be cancelled.
We keep two ready times on writes, one soft, with lazy writes, and another hard onw, with scheduled writes.
If a task requires a write during the lazy write, we cancel it and move it to later point in time.
